Transfer Learning in Multimodal Compositional and Relational Reasoning

### 2019-11-15 cvpr_submission/experiments.tex
Specify distinction of finetuning + comment paragraph in experiments.

The final set of experiments we consider is related to feature transfer.
The CoGenT-A \& -B sets of CLEVR differ by the available combinations of 8 object color attributes.
The colors are partitioned into two complementary families: 
Gray, Blue, Brown and Yellow in Family A and Red, Green, Purple, Cyan in Family B. 
The cubes and cylinders take colors from complementary families in each dataset with opposite configurations while
the spheres can take any color (See~\cref{tab:cogent_conditions}). 
Considering the input domain to be the set of objects with all attributes values, both sets differ by their marginal distributions $P_S$ and $P_T$. We consider 2 experiments with SAMNet trained on CoGenT-A: An immediate test (\emph{zero-shot learning}) from A to B and a finetuning of a single epoch on 30k Conditions B samples (following~\cite{johnson2017inferring, mascharka2018transparency, perez2018film, marois2018transfer}). The results are available in~\cref{fig:CoGenT-B-results}.

>>>>

The final set of experiments we consider is related to feature transfer.
The CoGenT-A \& -B sets of CLEVR differ by the available combinations of 8 object color attributes.
The colors are partitioned into two complementary families: 
Gray, Blue, Brown and Yellow in \textbf{Family A} and Red, Green, Purple, Cyan in \textbf{Family B}. 
The cubes and cylinders take colors from complementary families in each dataset with opposite configurations while
the spheres can take any color (See~\cref{tab:cogent_conditions}). 
Considering the input domain to be the set of objects with all attributes values, both sets differ by their marginal distributions $P_S$ and $P_T$. We consider 2 experiments with SAMNet trained on CoGenT-A: An immediate test (\emph{zero-shot learning}) from A to B and a finetuning of a single epoch on 30k Conditions B samples (following~\cite{johnson2017inferring, mascharka2018transparency, perez2018film, marois2018transfer}). The results are available in~\cref{fig:CoGenT-B-results}.
